Commit Rater

### 2015-08-26 presentations/paper/methodology.tex

>>>>

\subsubsection{Above repository-level}
It may be of further interest to look at the averages of adherance to guidelines across multiple repos and thereby extrapolate some general statistics about ueage of the guidelines in the Git community. But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.
